%\cvsection{Highlight Courses}{\faBook}
%
%\begin{itemize}
%	\item Pattern Recognition
%	\item Agile Programming
%	\item Linear Algebra
%	\item Risk Management
%	\item Machine Learning
%\end{itemize}

\cvsection{Career Objective}{\faBarChart}

As\, a\, person\, who\, interested\, in\, programming,\, mathematic,\, economics,\, and\, stock\, market,\, I\, can't\, help\, but\, find\, myself\, dream\, of\, becoming\, an\, Hedge\, Fund\, Manager.\, 
I\, love\, how\, the\, stock\, market\, is\, a\, competitive\, strategy\, game.\, The\, challenge\, of\, making\, decisions\, to\, outsmart\, the\, other\, investors\, drives\, me\, to\, achieve\, more.


%\cvachievement{\faCertificate}{Pattern Recognition}{}
%
%\cvachievement{\faCertificate}{Agile Programming}{}
%
%\cvachievement{\faCertificate}{Linear Algebra}{}
%
%\cvachievement{\faCertificate}{Risk Management}{}


\bigskip


\cvsection{Achievement}{\faTrophy}

\cvachievement{\faBookmark}{ACM-ICPC Programming Contest}{Multi-tiered competitive programming among the universities of the world.}
\begin{itemize}
	\item $15^{th}$ Place out of 100 teams, ACM-ICPC Thailand National Programming Contest 2015.
	\item $37^{th}$ Place out of 67 teams ($12^{th}$ out of 38 Thailand teams), ACM-ICPC Asia Phuket Regional Programming Contest 2015.
\end{itemize}

\divider

\cvachievement{\faBookmark}{Stock Trading Algorithm}{Senior Project.}
\begin{itemize}
	\item Using Online Machine Learning to progressively adjust level of trust on each Technical Indicators.
	\item Using Capital Asset Pricing Model to manage portfolio based on acceptable level of risk.
	\item Using Support Vector Machine to predict a trend of stock price.
\end{itemize}

\bigskip

\cvsection{Interest}{\faThumbsUp}

\wheelchart{1.5cm}{0.5cm}{%
	6/5.5em/Red!100/Machines Learning, 
	5/9em/Yellow!100/Risk\\ Management,
	4/6em/Green!100/Economics,
	2/6em/Blue!100/Psychology,
	2/5em/Purple!100/Consultant
}

\bigskip

%\cvsection{Sports}{}
%
%\wheelchart{1.5cm}{0.5cm}{%
%	8/4em/Red!100/Ice Skating,
%	5/8em/Green!100/Badminton,
%	4/4em/Blue!100/Archery,
%	6/8em/Yellow!100/Swimming 
%}
%%	8/4em/Red!80/Ice Skating,
%%	5/8em/Green!60/Badminton,
%%	4/4em/Blue!50/Archery,
%%	6/8em/Yellow!90/Swimming 
%
%\bigskip


\cvsection{Languages}{\faComments}

\medskip

\cvskill{Thai}{5}

\divider

\cvskill{English}{4}
